Depression and suicidality as costly signals of need

### 2021-04-02 Paper.rmd
Added m1 and m3 glmmboot models. Worked on methods section.

tar_load(
  c(
    'd',
    'power_curve',
    'power_curve2',
    'models',
    'models_prereg',
    'effect_sizes',
    'effect_sizes2',
    'effectsPlots', 
    'ecdf_plot',
    'plot_T1Belief_T1Action',
    'plot_emotions',
    'plot_raw_beliefs',
    'plot_raw_actions',
    'plot_raw_belief_action2d',
    'med1b',
    'med4',
    'm1b_boot',
    'm3b_boot',
    'dfT1emotion_vignette',
    'dfT1emotion_signal',
    'dfT2emotion_signal'
    )
  )

@@

## notes: 
add funding info somewhere
Find a place for the predictions and preregistration 
go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
add conclusion

@@

https://osf.io/g3s6n

@@

Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools[@NeckaEtAl2016, Robinson et al. 2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016]. For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design (Aguinis et al. 2020; Huang et al. 2015; Kennedy et al. 2020; Thomas and Clifford 2017).

@@

## Confirmatory Analyses

We used linear regression to analyze our results for the main effect of signal on belief in need and likelihood of help, controlling for baseline levels of belief in need and likelihood of help. (Need more detail)

Belief in need t2 ~ Signal + Belief in need t1
Likelihood of help t2 ~ Signal + Likelihood of help t1

Based on advice from our statistical consultant, we also fit the following interaction models:

Belief in need t2 ~ Signal * Belief in need t1
Likelihood of help t2 ~ Signal * Likelihood of help t1

The rationale for the interaction is that for individuals who indicate high levels of belief and helping at baseline, the signals might have reduced effect.

To examine our hypothesis that beneficial treatment would be largely due to a signal's positive impact on the participant's beleif in need we ran the following mediaton models for each pairwise combination of signals:

Mediator model: Belief in need t2 ~ Signal + Belief in need t1
Outcome model: Likelihood of help t2  ~ Signal + Belief in need t2 + Likelihood of help t1 + Belief in need t1

@@

```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively, with an interaction between T1 values and the signal. Fit using generalized linear regression models with the quasibinomial family."}
(effectsPlots$m1bplot + theme(axis.text.x = element_blank()))/effectsPlots$m3bplot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
```

@@

We estimated power using our pilot study data to compared the effect of the *Depression* signal vs. the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model. Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200. Power was computed as the proportion of p-values < 0.05. Power was about 80% for a sample size of about `r pwr80_90[2,2]`, and was about 90% for a sample size of about `r pwr80_90[2,3]`. We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request). Power was about 80% for a sample size of about `r pwr80_90[1,2]`, and was about 90% for a sample size of about `r pwr80_90[1,3]`. See Figure \@ref(fig:power).

>>>>

tar_load(
  c(
    'd',
    'signaling2018',
    'power_curve',
    'power_curve2',
    'models',
    'models_prereg',
    'effect_sizes',
    'effect_sizes2',
    'effectsPlots', 
    'ecdf_plot',
    'plot_T1Belief_T1Action',
    'plot_emotions',
    'plot_raw_beliefs',
    'plot_raw_actions',
    'plot_raw_belief_action2d',
    'med_prereg',
    'med1',
    'med1b',
    'med4',
    'med4b',
    'm1_boot',
    'm3_boot',
    'm1b_boot',
    'm3b_boot',
    'dfT1emotion_vignette',
    'dfT1emotion_signal',
    'dfT2emotion_signal'
    )
  )

@@

## notes: 
add funding info somewhere
Find a place for the predictions and preregistration 
go back and emphasize conflict and PI in the methods (at least in the pilot studies portion)
add abstract
add conclusion

@@

We preregistered four OLS linear regression models and one mediation model (https://osf.io/g3s6n). The first two regression models tested the effects of our ordinal signal variable on Time 2 *Belief* and *Action*, controlling for T1 *Belief* and *Action*, respectively (a pre-test/post-test design):

`r extract_eq(models_prereg$Model$m1, intercept='beta', wrap=T)`
`r extract_eq(models_prereg$Model$m3, intercept='beta', wrap=T)`

The second two models added interaction terms between signal and T1 *Belief* and *Action*, with the rationale that the signals might have reduced effect for individuals who indicate high levels of belief and helping at baseline:

`r extract_eq(models_prereg$Model$m1b, intercept='beta', wrap=T)`
`r extract_eq(models_prereg$Model$m3b, intercept='beta', wrap=T)`

The mediation model is in Figure \@ref(fig:medmodel):

Specifically, the mediation and outcome models, respectively, are:

`r extract_eq(med_prereg$model.m, intercept='beta', wrap=T)`
`r extract_eq(med_prereg$model.y, intercept='beta', wrap=T)`

For reasons we explain in the *Statistical methods* section, we report the OLS models in the Supplementary Information (SI), and in the Results section instead report conceptually equivalent generalized linear regression models (GLMs).

## Power analysis

The current study is a refinement of a pilot study (N=`r nrow(signalingdata2018)`) with very similar signals and outcomes. We used these pilot data to estimate the sample sizes needed to detect an effect of the *Depression* vs. *Verbal request* signal (two conditions) on *Belief* in the victim's need. Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`. We also estimated the sample size needed to detect an effect of *Depression* vs. a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request). Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`. See Figure \@ref(fig:power). Given our $1500 USD budget, we aimed for a sample size of 125 for two conditions, and 1250 for all conditions in the study. For more details, see the SI and XX.

@@

Overall, the quality of data provided by MTurk workers tends to resemble that of university sample pools [@NeckaEtAl2016, Robinson et al. 2019], with there being some indication that it might outperform university samples due to its previously mentioned diversity (Thomas and Clifford 2017) or the overall attentiveness of turkers [@HauserSchwarz2016]. For this reason, concerns about data quality come primarily from the threat of bot use or respondents faking their location to take surveys in a language they do not understand well, with there being little evidence of the former [@KennedyEtAl2018] and the risk of the latter able to be minimized through well designed attention checks, timed responses, or general study design (Aguinis et al. 2020; Huang et al. 2015; Kennedy et al. 2020; Thomas and Clifford 2017).

@@

## Statistical analyses

Our pre-test and post-test measures, *T1 & T2 Belief* and *T1 & T2 Action*, were all measured on a 0-100 point scale, which we rescaled to 0-1. A substantial number of participants rated their beliefs and actions as exactly 0 or exactly 1 at either T1 or T2. OLS linear regression models are not suitable for a closed and bounded distribution with so many values on the boundary because the residuals would not be normally distributed or have constant variance. Beta regression, a possible alternative, is only defined on the open interval, (0, 1), whereas our data had many values on the boundaries (a closed interval). A variant of beta regression, zero-one inflated beta, is inappropriate because it assumes separate processes for the generation of data on the boundaries vs. the interior, and we had no reason to believe that our zeros and ones were generated by a different process than the rest of our observations.

We therefore fit models of our two outcome variables in three ways. First, we used fractional regression models, introduced in a seminal paper by @papke1996 for outcomes on [0, 1], which, in brief, involve fitting a quasi-likelihood version of logistic regression with robust standard errors. This method is implemented in the R `frm` package [@ramalho2019]. Second, we fit GLM logistic regression models, computing 95% CI's via bootstrapping, using the R `glmmboot` package created to model outcomes on [0, 1] [@humphrey2020]. Finally, we fit GLM models with the quasibinomial family and logit link using the `glm` function in R stats library. The estimated coefficients, standard errors, and confidence intervals produced by the three methods were *very* similar, and often identical. We therefore proceeded to fit models using `glm` with the quasibinomilal family and logit link because model objects produced by this function are compatible with numerous other R packages for estimating and plotting effects.

Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which transforms [0, 1] to (-$\infty$, $\infty$). We therefore only included it if there was clear evidence of superior fit. Our intervention was *signal*, coded as an ordinal variable with the following preregistered rank order: verbal request, crying, mild depression, depression, suicide attempt. We used the default `glm` settings, which code such variables as orthogonal polynomial contrasts. Our primary confirmatory regression models were as follows (where the signal subscripts indicate polynomial degree):

`r extract_eq(models$Model$m1, intercept='beta', wrap=T)`
`r extract_eq(models$Model$m3, intercept='beta', wrap=T)`

To test our hypothesis that the likelihood of acting to help the victim would be largely mediated by a signal's positive impact on the participant's beleif in the victim's need, we used the `mediation` package [@tingley2014] to fit a mediaton model for *Depression* vs. *Verbal request*. The mediation and outcome models, respectively, were:

`r extract_eq(med1$model.m, intercept='beta', wrap=T)`
`r extract_eq(med1$model.y, intercept='beta', wrap=T)`

@@

```{r beliefeffect, fig.width=8, fig.height=8, fig.cap="The effect of the signals on T2 Belief (top) and Action (bottom) controlling for T1 values of Belief and Action, respectively. Fit using generalized linear regression models with the quasibinomial family."}
(effectsPlots$m1plot + theme(axis.text.x = element_blank()))/effectsPlots$m3plot + plot_layout(ncol = 1) & theme(plot.margin = unit(c(0,0,0,0), units = 'mm'))
```

@@

We estimated power using our pilot study data to compare the effect of the *Depression* signal vs. the *Verbal request* signal on *Belief* (that the sister needed the money) at T2 controlling for *Belief* at T1 in a linear regression model. Specifically, we resampled the pilot data with replacement, fit the linear regression model, and extracted the p-value for the signal coefficient, repeating this 2000 times for each sample size ranging from N=20 to N=200. Power was computed as the proportion of p-values < 0.05. Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`. We then repeated this entire procedure to compare *Depression* to a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request). Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`. See Figure \@ref(fig:power).
